Uneven Investments in Toronto's Wards

### 2024-09-27 paper/paper.qmd
Update summary table to include ward number and name

@@

# Select relevant columns for the table
merged_table_select <- merged_data |>
  select(
    `Ward Number`,
    per_capita_funding,
    `Median total income of households in 2020 ($)`,
    `Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`,
    `Bachelor’s degree or higher per capita`,
    `Total visible minority population per capita`
  )

@@

# Create the table with kable and apply enhanced styling
kable(
  merged_table_2, 
  escape = TRUE,                   
  col.names = c(
    "Ward Number", 
    "Per Capita Funding", 
    "Household Median Income", 
    "Low Income Prevalence", 
    "Bachelor’s Degree or Higher", 
    "Visible Minority Population"
  )
) |>
  kable_styling(
    bootstrap_options = c("condensed"),  
    full_width = FALSE,  
    position = "left",  
    font_size = 7 
  ) |>
  add_footnote("Rows in red indicate a ward where the Household Median Income is $84,000 or less", notation="alphabet") |>
  column_spec(1, width = "2cm") |>
  column_spec(2:3, width = "3cm") |>
  column_spec(4, width = "2cm") |>
  column_spec(5:6, width = "3cm") |>
  row_spec(1, color = "red") |>
  row_spec(6, color = "red") |>
  row_spec(9:10, color = "red") |>
  row_spec(13:14, color = "red") |>
  row_spec(17:19, color = "red") |>
  row_spec(21:24, color = "red")
```

>>>>

# Create a data frame with Ward Names 
ward_names_df <- data.frame(
  `Ward Number` = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 
                    11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 
                    21, 22, 23, 24, 25),
  `Ward Name` = c("Etobicoke North", "Etobicoke Centre", "Etobicoke—Lakeshore", "Parkdale—High Park", "York South—Weston", "York Centre",
                "Humber River—Black Creek", "Eglinton—Lawrence", "Davenport", "Spadina—Fort York", "University—Rosedale", "Toronto—St. Paul's", "Toronto Centre", "Toronto—Danforth", "Don Valley West", "Don Valley East", "Don Valley North", "Willowdale", "Beaches—East York", "Scarborough Southwest", "Scarborough Centre", "Scarborough—Agincourt", "Scarborough North", "Scarborough Guildwood", "Scarborough—Rouge Park"),
  check.names = FALSE
)

# Join ward names into marged data
merged_data <- merged_data |>
  left_join(ward_names_df, by = "Ward Number")

@@

# Create a combined Ward column
merged_data <- merged_data |>
  mutate(`Ward` = paste(`Ward Name`, "-", `Ward Number`))

# Select relevant columns for the table
merged_table_select <- merged_data |>
  select(
    `Ward`, 
    per_capita_funding,
    `Median total income of households in 2020 ($)`,
    `Prevalence of low income based on the Low-income measure, after tax (LIM-AT) (%)`,
    `Bachelor’s degree or higher per capita`,
    `Total visible minority population per capita`
  )

@@

# Create the table with kable and apply enhanced styling
kable(
  merged_table_2, 
  escape = TRUE,                   
  col.names = c(
    "Ward Name - Number", 
    "Per Capita Funding", 
    "Household Median Income", 
    "Low Income Prevalence", 
    "Bachelor’s Degree or Higher", 
    "Visible Minority Population"
  )
) |>
  kable_styling(
    bootstrap_options = c("condensed"),  
    full_width = FALSE,  
    position = "left",  
    font_size = 7 
  ) |>
  add_footnote("Rows in red indicate a ward where the Household Median Income is $84,000 or less", notation="alphabet") |>
  column_spec(1, width = "2cm") |>
  column_spec(2:3, width = "3cm") |>
  column_spec(4, width = "2cm") |>
  column_spec(5:6, width = "3cm") |>
  row_spec(1, color = "red") |>
  row_spec(6, color = "red") |>
  row_spec(9:10, color = "red") |>
  row_spec(13:14, color = "red") |>
  row_spec(17:19, color = "red") |>
  row_spec(21:24, color = "red")
```
